Figure 3-Supplement 1

### 2017-12-11 inst/lnc34a/lnc34a.Rmd
adding prelim data documentation

The results show a high density of CAGE tags aligning to the region corresponding to the annotated miR34a asRNA start site. Several additional peaks, albeit with a much lower average expression, aligns slightly upstream of the annotated miR34a asRNA start site, one of which, corresponds to the upstream start site detected in our primer walk analysis (**Figure 1e**). Despite this, we find no CAGE tags aligning at the transcription start site or upstream of the transcription start site of the lnc34a transcript. This potentially indicates that lnc34a is tightly regulated and specifically expressed in the CCSC context, as claimed by the authors. An alternative intrepretation could be that lnc34a expression is present in a subset of the examined cell lines although at too low levels to be detected. Finally, lnc34a may not be 5'-capped precluding its detection by CAGE.

In order to lnc34a expression in a manner that is not dependant on 5'-capping, we proceeded to examine spliced RNA sequencing reads from 36 cell lines, taking advantage of the fact that lnc34a has an exon which is not present in any miR34a asRNA isoforms.

@@

These results indicate that, although splice junctions corresponding to multiple isoforms detected by PCR cloning of the miR34a asRNA were detected, the data give no support for the presence of the splice junction between the first and second exon of lnc34a. In summary, these results indicate that lnc34a expression may be confined to colon cancer stem cells as evidence for its expression in the examined cell lines is not forthcomming.

In addition, we note several comments in the public review that was published in conjunction with the work by Wang et al. The authors mention, and provide data, indicating that lnc34a expression is not changed upon ectopic expression of TP53. In contrast, miR34a asRNA is strongly regulated by TP53 as the evidence shows in this and others (Léveillé 2015, Rashi-Elkeles 2014, Hünten 2015, Ashouri 2016, Kim 2017) findings.

Furthermore, Wang et al. also mention in the public review that lnc34a has a low expression level in HCT116 cells although we detect robust expression of miR34a asRNA in this cell type (**Figure 1b**).

In summary, these results indicate that lnc34a expression is not present in the cell types examined where there exists strong evidence for the presence miR34a asRNA. For these reasons, we believe miR34a asRNA and lnc34a to be individual antisense RNA transcripts.

>>>>

The results show a high density of CAGE tags aligning to the region corresponding to the annotated miR34a asRNA start site. Several additional peaks, albeit with a much lower average expression, aligns slightly upstream of the annotated miR34a asRNA start site, one of which, corresponds to the upstream start site detected in our primer walk analysis (**Figure 1e**). Despite this, we find no CAGE tags aligning at the transcription start site or upstream of the transcription start site of the lnc34a transcript. This potentially indicates that lnc34a is tightly regulated and specifically expressed in the CCSC context, as suggested by the authors. An alternative intrepretation could be that lnc34a expression is present in a subset of the examined cell lines although at too low levels to be detected. Finally, lnc34a may not be 5'-capped precluding its detection by CAGE.

In order to lnc34a expression in a manner that is not dependant on 5'-capping, we proceeded to examine spliced RNA sequencing reads from 36 cell lines, taking advantage of the fact that lnc34a has an exon which is not present in any annotated or PCR cloned miR34a asRNA isoforms.

@@

These results indicate that, although splice junctions corresponding to multiple isoforms detected by PCR cloning of the miR34a asRNA were detected, the data give no support for the presence of the splice junction between the first and second exon of lnc34a. In summary, these results indicate that lnc34a is unlikely to represent the same asRNA transcript as miR34a asRNA and that its expression may be confined to colon cancer stem cells.

In addition, there are several other lines of evidence indicating that the asRNA described in our paper is distinct from lnc34a. We noted several comments in the public review that was published in conjunction with the work by Wang et al. that the authors mention, and provide data, indicating that lnc34a expression is not changed upon ectopic expression of TP53. In contrast, miR34a asRNA is strongly regulated by TP53 as the evidence shows in this and others findings (Léveillé 2015, Rashi-Elkeles 2014, Hünten 2015, Ashouri 2016, Kim 2017). Furthermore, Wang et al. also mention in the public review that lnc34a has a low expression level in HCT116 cells although we detect robust expression of miR34a asRNA in this cell type (**Figure 1b**).

In summary, these results indicate that lnc34a expression is not present in the cell types examined where there exists strong evidence for the presence miR34a asRNA and, for these reasons, we believe miR34a asRNA and lnc34a to be individual antisense RNA transcripts.

### 2017-12-11 inst/stable_line_expression/stable_line_expression.Rmd
adding prelim data documentation

Two experimental (technical) replicates were included in each QPCR run and delta ct was calculated for each sample using the mean of the gene of interest's technical replicates and the house keeping gene's technical replicates. delta-delta ct was calculated for each sample by subtracting the median dct value for the corresponding mock samples. At least three independant experiments (biological replicates) were performed in total (see more below). The Student's t-test was used to compare the mock vs miR34a asRNA overexpressing group's delta-delta ct values for both genes.

The sample numbers for each group are as follows:
```{r}

n <- data.frame(
  name = c(
    "PC3 mock",
    "PC3 miR34a asRNA",
    "Skov3 mock",
    "Skov3 miR34a asRNA",
    "Saos2 mock",
    "Saos2 miR34a asRNA"
  ),
  n = c(5, 5, 4, 4, 5, 5)
)
n

>>>>

Two experimental (technical) replicates were included in each QPCR run and delta ct was calculated for each sample using the mean of the gene of interest's technical replicates and the house keeping gene's technical replicates. delta-delta ct was calculated for each sample by subtracting the median dct value for the corresponding mock samples. Five independant experiments were performed in total. The Student's t-test was used to compare the mock vs miR34a asRNA overexpressing group's delta-delta ct values for both genes.

### 2017-12-11 inst/stable_line_expression_hek293t/stable_line_expression_hek293t.Rmd
adding prelim data documentation

---
title: "Figure 3-Supplement 1"
subtitle: "miR34a asRNA stable over-expression cell lines compared to HEK293t"
author: "Jason T. Serviss"
date: "31/01/2017"
output:
  html_document:
    theme: flatly
    code_folding: hide
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

@@

Two experimental (technical) replicates were included in each QPCR run and delta ct was calculated for each sample using the mean of the gene of interest's technical replicates and the house keeping gene's technical replicates. Delta-delta ct was calculated for each sample by subtracting the median dct value for the corresponding untreated samples. Five independant experiments were performed in total for all cell lines with the exception of PC3. Six independant experiments were preformed for the PC3 cell lines although, one experiment was removed due to excessivley high ct values (>30) in the house keeping gene, indicating an insufficient amount of RNA to sucessfully detect the genes of interest.

>>>>

---
title: "Figure 3-Supplement 1"
subtitle: "miR34a asRNA stable over-expression cell lines compared to HEK293T"
author: "Jason T. Serviss"
date: "31/01/2017"
output:
  html_document:
    theme: flatly
    code_folding: hide
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

@@

Two experimental (technical) replicates were included in each QPCR run and delta ct was calculated for each sample using the mean of the gene of interest's technical replicates and the house keeping gene's technical replicates. Delta-delta ct was calculated for each sample by subtracting the median dct value for the corresponding untreated samples. Five independant experiments were performed in total for all cell lines.
